Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-16 arxiv/tools.tex
appendix

 \begin{corollary}\label{cor_calE}
Suppose the entries of $\cal E=[\epsilon^{(1)},\epsilon^{(2)},\cdots, \epsilon^{(t)}]\in \R^{n\times t}$ are i.i.d. random variables of mean zero, variance $\sigma^2$ and bounded moments up to any order. Then for any deterministic vector $v\in \R^n$ and deterministic $n\times n$ matrix $B\in \R^{n\times n}$, we have that with high probability,
\be\label{vcalE} |v^\top \epsilon^{(i)}| \le \sigma n^{c} \|v\|, \ee
and
\be\label{vcalA2} \left|(\epsilon^{(i)})^\top B \epsilon^{(j)} - \delta_{ij}\cdot \sigma^2 \tr(B)\right| \le n^{c} \|B\|_F ,\ee
for any small constant $c>0$. As a consequence, equations \eqref{vcalE} and \eqref{vcalA2} imply that 
\be\label{vcalAE3}
\|v^\top \cal E\| \le \sigma n^{c} \|v\|, \ \ \ \text{and}\ \ \ \left\| \cal E^\top B \cal E - \sigma^2 \tr(B)\cdot \id_{t\times t}\right\|_F \le n^{c} \|B\|_F ,
\ee
 with high probability for any small constant $c>0$.
 \end{corollary}
 \begin{proof}
Note that $\epsilon^{(i)}_j/\sigma$, $1\le i \le t,1\le j \le n$, are i.i.d. random variable of mean zero, variable one and bounded moments up to any order. Then using the first estimate in equation \eqref{eq largedev1}, we can obtain that $|v^\top \epsilon^{(i)}| = \Big|\sum_{j=1}^n v_j \epsilon^{(i)}_j \Big| \prec \sigma \|v\|,$  which concludes \eqref{vcalE} together with the definition of stochastic domination in Definition \ref{stoch_domination}. Similarly, using the second estimate in equation \eqref{eq largedev1}, we can obtain that for $i\ne j$,
 \begin{align*}
\left|(\epsilon^{(i)})^\top B \epsilon^{(j)}\right| = \Big|\sum_{k,l=1}^n \epsilon^{(i)}_k\epsilon^{(j)}_l B_{kl} \Big| \prec \sigma^2 \Big(\sum_{k,l}|B_{kl}|^2\Big)^{1/2}=\sigma^2 \|B\|_F.
 \end{align*}
Using the two estimates in equation \eqref{eq largedev2}, we obtain that 
\begin{align*}
\left|(\epsilon^{(i)})^\top B \epsilon^{(j)} - \delta_{ij}\cdot \sigma^2 \tr(B)\right| &\le \Big| \sum_{k=1} \left(|\epsilon^{(i)}_k|^2-\E|\epsilon^{(i)}_k|^2\right)B_{ii} \Big|+\Big| \sum_{ k\ne l } \epsilon^{(i)}_k \epsilon^{(i)}_l B_{kl} \Big| \\
&\prec \sigma^2 \Big( \sum_{k}|B_{kk}|^2\Big)+\sigma^2 \Big( \sum_{k\ne l}|B_{kl}|^2\Big)^{1/2}\lesssim \sigma^2 \|B\|_F.
\end{align*}
The above two estimates conclude  \eqref{vcalA2}. Finally, the estimates in equation \eqref{vcalAE3} are easy consequences of equations \eqref{vcalE} and \eqref{vcalA2} since $t$ is a fixed integer that does not change with $p$.
 \end{proof}

>>>>

 \begin{corollary}\label{cor_calE}
Suppose the entries of $\cal E=[\epsilon^{(1)},\epsilon^{(2)},\cdots, \epsilon^{(t)}]\in \R^{n\times t}$ are i.i.d. random variables of mean zero, variance $\sigma^2$ and bounded moments up to any order. Then for any deterministic vector $v\in \R^n$ and deterministic $n\times n$ matrix $B\in \R^{n\times n}$, we have that with high probability,
\be\label{vcalE} |v^\top \epsilon^{(i)}| \le n^{c} \cdot \sigma \|v\|, \ee
and
\be\label{vcalA2} \left|(\epsilon^{(i)})^\top B \epsilon^{(j)} - \delta_{ij}\cdot \sigma^2 \tr(B)\right| \le n^{c}\cdot \sigma^2 \|B\|_F ,\ee
for any small constant $c>0$. As a consequence, equations \eqref{vcalE} and \eqref{vcalA2} imply that 
\be\label{vcalAE3}
\|v^\top \cal E\| \le n^{c} \cdot \sigma  \|v\|, \ \ \ \text{and}\ \ \ \left\| \cal E^\top B \cal E - \sigma^2 \tr(B)\cdot \id_{t\times t}\right\|_F \le n^{c} \cdot  \sigma^2\|B\|_F ,
\ee
 with high probability for any small constant $c>0$.
 \end{corollary}
 \begin{proof}
Note that $\epsilon^{(i)}_j/\sigma$, $1\le i \le t,1\le j \le n$, are i.i.d. random variable of mean zero, variable one and bounded moments up to any order. Then using the first estimate in equation \eqref{eq largedev1}, we can obtain that $|v^\top \epsilon^{(i)}| = \Big|\sum_{j=1}^n v_j \epsilon^{(i)}_j \Big| \prec \sigma \|v\|,$  which concludes \eqref{vcalE} together with the definition of stochastic domination in Definition \ref{stoch_domination}. Similarly, using the second estimate in equation \eqref{eq largedev1}, we can obtain that for $i\ne j$,
 \begin{align*}
\left|(\epsilon^{(i)})^\top B \epsilon^{(j)}\right| = \Big|\sum_{k,l=1}^n \epsilon^{(i)}_k\epsilon^{(j)}_l B_{kl} \Big| \prec \sigma^2 \Big(\sum_{k,l}|B_{kl}|^2\Big)^{1/2}=\sigma^2 \|B\|_F.
 \end{align*}
Using the two estimates in equation \eqref{eq largedev2}, we obtain that 
\begin{align*}
\left|(\epsilon^{(i)})^\top B \epsilon^{(j)} - \delta_{ij}\cdot \sigma^2 \tr(B)\right| &\le \Big| \sum_{k=1} \left(|\epsilon^{(i)}_k|^2-\E|\epsilon^{(i)}_k|^2\right)B_{ii} \Big|+\Big| \sum_{ k\ne l } \epsilon^{(i)}_k \epsilon^{(i)}_l B_{kl} \Big| \\
&\prec \sigma^2 \Big( \sum_{k}|B_{kk}|^2\Big)+\sigma^2 \Big( \sum_{k\ne l}|B_{kl}|^2\Big)^{1/2}\lesssim \sigma^2 \|B\|_F.
\end{align*}
The above two estimates conclude  \eqref{vcalA2}. Finally, the estimates in equation \eqref{vcalAE3} are easy consequences of equations \eqref{vcalE} and \eqref{vcalA2} since $t$ is a fixed integer that does not change with $p$.
 \end{proof}
